\section{Motivation and background$^\dagger$}
\label{alg:zon_calculation}
The \emph{Multi-Agent Programming Contest} is an annual online programming contest hosted by the Clausthal University of Technology since 2005.
Participation is free to any interested groups.
There are no monetary rewards for the winning groups.
The aim of the MAPC is to promote academic interest in the field  of multi-agent systems, that is, systems in which multiple artificial agents have to collaborate to achieve a goal.

The nature of the task in which the agents compete in the MAPC has changed over the years, but since 2011 it has been the same \enquote{Agents on Mars} scenario, which will be described below.
The winner and further rankings of each year's contest are determined by having each group's agent face off against the other in a tournament, and awarding points to each team according to their performance in each match.

\subsection{The \enquote{Agents on Mars} scenario$^\dagger$}
The \enquote{Agents on Mars} scenario is the one that has been used in the yearly MAPC since 2011.
In it, two opposing teams of agents are placed on nodes in a randomized graph.
Each node in the graph has a value which is used for scoring, and agents can traverse the graph by moving along the edges connecting the nodes.
The \enquote{Agents on Mars} name relates to the fictional background \enquote{story} of the scenario: Man has populated Mars, and must find and occupy wells of water on the surface of the planet and protect them from \enquote{pirates}.

The simulation is turn-based, and each agent can perform one action per turn.
There are 28 agents in each team, and each agent belongs to one of five different agent classes, and the agent's type determines the kind of actions the agent can perform and other values used to further differentiate agent classes.
The goal of each match is to have a higher score than the opponent's team at the end of a predetermined number of steps (400 in the 2014 MAPC).
A high score is achieved by finding localized parts of the graph which contain high-value nodes, surrounding these \enquote{zones} with one's own agents, and protecting them from enemy agents' attacks.
The full background story, as well as the more detailed official description of the scenario, can be found in the scenario description provided by the MAPC organizers~\cite{ahlbrecht_mapc_2014}.

\subsection{The \emph{MAKo} (Multi-Agents Koblenz) team$^\dagger$}
The German University of Koblenz-Landau participated in the 2014 MAPC with a small team of graduate students in the scope of a research lab.
The students who participated in research lab until its end were Artur Daudrich, Sergey Dedukh, Manuel Mittler, Michael Ruster, Michael Sewell and Yuan Sun.
The research lab consisted of an initial seminar phase and the longer project phase, where the students designed and implemented the multi-agent architecture used to participate in the MAPC.