\subsection[Structure and Meetings]{Structure and Meetings$^{\odot/\circ}$}
At the beginning of the project the team had to define a structure for collaboration.
We decided to have a flat hierarchy with all members as part of dynamically built, small development teams.
Michael Ruster was selected as a project leader with his role mainly focussed on organisation.
He carried out the external communication with the supervisors and contest organisers.
The project leader was also responsible for configuring the server and running test simulations together with the organisers of the MAPC as well as running the final simulations.
His leadership followed a democratic management style, so decisions were made by the team as a whole through majority decisions.
Once in every week, the team met in person to discuss the current progress and the upcoming course of actions.
During these meetings, many of our algorithms were initially developed and discussed.
At the end of each meeting, tasks were worked out and assigned to dynamic groups to be solved up to the next meeting.
These groups mainly consisted of two or three people with more people working on tasks we found to be more important.
Team members were assigned for a specific task due to personal interest or expertise.
In the beginning, we also tried some hacking sessions, but quickly found out that working from home worked best for us.
This was advantageous because no fixed timeslots needed to be found.
Instead, everybody would work independently when they found the time while staying in contact with the others through chat or voice over IP.
If there was need for reconciliation, for example when tasks of different groups were closely interrelated or dependant on one another, short-termed Skype calls were held.
To the end of development, the groups diverged mainly into Artur Daudrich and Michael Sewell working on the Java-side of our code and the rest focussing on implementations in AgentSpeak(L).
The prior group hence concentrated on doing background calculations like internally modelling and constructing the graph and environment design.
Accordingly, Manuel Mittler, Michael Ruster, Sergey Dedukh and Yuan Sun focussed more on agent programming and developing strategies.
