% I've put this section first so the later chapters can already rely on the reader knowing what the scenario is about. Furthermore, we can then directly rule out concepts which we are presenting by applying them theoretically onto the scenario/our needs.
This section and its subsections introduce the Multi-Agent Programming Contest (short: \emph{MAPC}).
It is an international online competition which started in 2005 and took place every year since then.
This tournament is held as an online event in the sense that all participants run their systems locally and communicate with the contest server via Internet.
The winning team is determined by each team playing against all other teams three times.
All participants are free to choose which technologies and implementations they want to use for building their multi-agent system upon.
The scenario of the MAPC has changed several times over the years:
\begin{itemize}
	\item 2005: Food Gatherers
	\item 2006-07: Gold miners
	\item 2008-10: Cows and Cowboys
  \item Since 2011: Agents on Mars
\end{itemize}
The scenarios became more and more complex as the agents' features were extended and heterogeneous agent roles were added~\cite{behrens_multi-agent_2012}. % 113

\autoref{fun:mapc_general} describes 2014's \mars{} briefly.
It covers the story motivating the scenario, the goals of the scenario and the representation of the environment.
Furthermore, it presents how team scores are calculated in the competition.
\autoref{fun:mapc_roles} addresses the agents and the actions which they may execute.
The focus of the section is to explain all executable actions and their effects.
Thereby, the agent-specific roles of the \mars{} and their differences are covered.

\input{content/fundamentals/mapc_general.tex}

\input{content/fundamentals/mapc_roles.tex}
