\documentclass{../tech_reports/template/llncs}
%
\usepackage{url}
\usepackage{amsmath} % use equations
\usepackage{amssymb} % Let Sun have a black triangle
\usepackage{graphicx} % allow PNGs as graphics
\usepackage{epstopdf} % Call epstopdf "on the fly"
\usepackage{tabularx} % adds X alignment and allows \textwidth width for tables
\def\arraystretch{1.5} % add some padding to table cells
\usepackage[labelfont=bf]{caption} % bold labels for Table, Figure etc.
\RequirePackage[utf8]{inputenc} % support Umlauts and special characters
\usepackage{microtype} % use space more efficiently and hyphenate smarter: all in all looks a lot sexier
\newcommand\blfootnote[1]{%
    \begingroup
    \renewcommand\thefootnote{}\footnote{#1}%
    \addtocounter{footnote}{-1}%
    \endgroup
}
\usepackage{listings} % allow source code environment
\lstset{ % make tildes readable in lstlistings
      literate={~} {$\sim$}{1}
}
\lstdefinestyle{flux} { % custom syntax highlighting for FLUX
  frame=L,
  xleftmargin=\parindent,
  basicstyle=\footnotesize\ttfamily,
  breakatwhitespace=true,
  numbers=left,
  escapechar=\%,
  numberstyle=\tiny,
  numberblanklines=false,
  captionpos=b,
  emph={perform, poss, state\_update, main\_loop, init},
  emphstyle=\textbf,
}
\lstset{style=flux} % activate flux syntax highlighting in listings
\usepackage[detect-all,round-mode=places]{siunitx} % A comprehensive (SI) units package
\usepackage{latexsym} % allows special symbols
\usepackage{graphicx} % enables figures
\usepackage{caption} % Support for captions
\usepackage{subcaption} % Support for sub-captions
\usepackage{csquotes} % Context sensitive quotation facilities
\usepackage{booktabs} % Publication quality tables in LaTeX
\usepackage{todonotes} % Mark­ing things to do in a LaTeX doc­u­ment
\usepackage[backend=biber,url=false]{biblatex} % Bibliographies in LaTeX using BibTeX for sorting only
\addbibresource{content/sources.bib}
\usepackage[pdfdisplaydoctitle,linkcolor=theblue,citecolor=theblue,urlcolor=thered]{hyperref} % Extensive support for hypertext in LaTeX (load last)
\RequirePackage[hyphenbreaks]{breakurl} % allow hyphenation in URLs
\usepackage{cleveref} % Intelligent cross-referencing, load after hyperref
% Make autoref talk about lines in lstlistings:
\def\lstnumberautorefname{Line}
% Make autoref start (sub-(sub-))sections with a capital S
\def\sectionautorefname{Section}
\def\subsectionautorefname{Section}
\def\subsubsectionautorefname{Section}
% Fancy headers and footers to add the page number:
\makeatletter
\providecommand\phantomcaption{\caption@refstepcounter\@captype}
\makeatother
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{
  \fancyhead[L]{\rightmark}
  \fancyhead[R]{\thepage}
}
%
\title{Research Lab \enquote{Multi-Agent Programming Contest 2014}}
\subtitle{Final Report}
%\titlerunning{logprog}
\author{Artur Daudrich$^{\star}$ \and Sergey Dedukh$^{\diamond}$ \and Manuel Mittler$^{\odot}$ \and Michael Ruster$^{\circ}$ \and Michael Sewell$^{\dagger}$ \and Yuan Sun$^{\blacktriangle}$\blfootnote{The symbols after the authors' names indicate who wrote which section.
  When there are multiple symbols, it means that the first part of author(s) wrote it and the second part significantly corrected/updated and proofread it.
  E.g.\ $^{\star/\odot,\dagger/\blacktriangle}$ would indicate $^{\star}$ and $^{\odot}$ are the authors and $^{\dagger}$ and $^{\blacktriangle}$ corrected it.}}
\institute{University of Koblenz-Landau, Campus Koblenz}
%
\newcommand{\mars}{\enquote{Agents on Mars} scenario}
\begin{document}
\maketitle
\pagenumbering{roman}
\tableofcontents
\clearpage
\pagenumbering{arabic}

\section[Motivation and Background]{Motivation and Background$^\dagger$}
\todo{The subsections are quite short. We probably should merge them later on. Also, we'll have to take a look of just about how much we want to talk about the MAPC Mars scenario at this point already. If we keep it as general as we currently are, this will probably be fine. Within the fundamentals part, we can then talk about agents, actions, roles, attributes, what is a zone and so forth.}
\input{content/motivation.tex}

\section{Scientific Background and Fundamentals}
\input{content/fundamentals.tex}

\section{Algorithms and Strategies}
\input{content/algorithms.tex}

\section[The BDI Model in Jason and our Implementation]{The BDI Model in Jason and our Implementation$^{\blacktriangle,\circ}$}\label{imp:BDI_AS}
\input{content/implementation/BDI_AS}

\section[Team Organisation and Individual Tasks]{Team Organisation and Individual Tasks$^{\blacktriangle/\circ}$}
\input{content/organisation.tex}

\section[Discussion and Conclusion]{Discussion and Conclusion $^{\circ}$}
In this last part, we reflect on the actual competition as well as our work.
First, \autoref{con:competition} presents the setup and procedure of the competition.
The results of the competition are presented.
Moreover, some general observations we made while monitoring the behaviour of our agents throughout the matches are given.
\autoref{con:learned} builds upon these observations by explaining in more detail what we saw and which conclusions can be drawn from this.
Besides, the Section also discusses more general lessons we have learned while developing our multi-agent system.
\input{content/conclusion.tex}

%\bibliographystyle{../tech_reports/template/splncs03}
%\clearpage
%\bibliography{./content/sources}
\printbibliography
\end{document}
